A large-scale analysis of racial disparities in police stops across the United

### 2019-12-11 lib/paper_results.Rmd
changes that didn't get merged on last push
Add robustness checks to mj tt priors

```{r mj_inferred_threshold_plot, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes
```

>>>>

```{r mj_inferred_threshold_plot, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1$plot
```

Prior robustness checks

Scaling factor 0.5:

WA rhat = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$metadata$wa_rhat`

WA n_eff = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$metadata$wa_n_eff`

CO rhat = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$metadata$co_rhat`

CO n_eff = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$metadata$co_n_eff`

```{r mj_inferred_threshold_plot_0.5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_0.5$plot
```

Scaling factor 1.5:

WA rhat = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$metadata$wa_rhat`

WA n_eff = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$metadata$wa_n_eff`

CO rhat = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$metadata$co_rhat`

CO n_eff = `r mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$metadata$co_n_eff`

```{r mj_inferred_threshold_plot_1.5_prior_scale, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1.5$plot
```
